\documentclass[a4paper,12pt]{article}

\include{cv-commands2}
\usepackage{hyperref, color}
\hypersetup{
bookmarks=false,
pdfauthor={Charles Julian Knight},
pdftitle={R\'{e}sum\'{e}},
colorlinks=true,
urlcolor=black,
}
\begin{document}
\oddsidemargin=-1cm
\setmainfont

\header
{\LARGE{Charles Julian Knight}}
{{\hspace{.08in}\small \href{mailto:julian@rabidaudio.com}{\textcolor{red}{julian@rabidaudio.com}}}\\
\hspace{0in} \scriptsize \url{http://www.linkedin.com/pub/charles-knight/27/b96/907}}
{330 Valley Green Dr.\\Atlanta, GA 30342\\
{404 585 1386}\\ %{\href{mailto:charles@rabidaudio.com}{\textcolor{red}{charles@rabidaudio.com}}}\\
}\\
%\begin{center}\footnotesize{\textit{My objective is to get a summer internship as an engineer at a local Atlanta technology startup.}}\end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
\resumeitem{Georgia Institute of Technology}{B.S. Electrical Engineering}{$\hspace{.25in}$Fall 2012 - Spring 2015 (expected)} %\hspace{40px} GPA: 3.06
\largeskip \largeskip
\resumeitem{Berry College}{B.A. Dual-Degree Program}{$\hspace{.24in}$Fall 2009 - Spring 2012} %\hspace{85px} GPA: 2.94
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Organizations}
\resumeitem{\href{http://startupexchange.gatech.edu/}{Startup Exchange}}{} \footnotesize{\textit{Student organization to foster entrepreneurship and hacker culture on campus. Co-led the Maker team. Developed and maintained websites, taught classes on web development with Ruby on Rails, organized and attended hackathons. }}

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Technical skills}

%\resumeitem{Certifications}{ Technical Certifications {\footnotesize \begin{itemize}
%\item CompTIA A+ 2009
%\item CompTIA Network+
%%\item CompTIA Linux+ (in progress)
%\item IC3 Computing Core
%\end{itemize}}}
%\largeskip

\resumeitem{Programming}{Familiar with:\\ \footnotesize
\begin{left}
\hspace{1.58in}
	\begin{tabular}{lll}
		$\bullet \hspace{.05in}$ Javascript (MEAN, jQuery) & $\hspace{.05in} \bullet \hspace{.05in}$ Ruby & $\hspace{.4in} \bullet \hspace{.05in}$ Python \\
		$\bullet \hspace{.05in}$ Perl & $\hspace{.05in} \bullet \hspace{.05in}$ PHP & $\hspace{.4in} \bullet \hspace{.05in}$ Embedded C/C++ \\
	\end{tabular}
\end{left}
}
\largeskip

%\resumeitem{Operating Systems}{Familiar with:\\ \footnotesize
%\begin{left}
%\hspace{1.58in}
%	\begin{tabular}{lll}
%		$\bullet \hspace{.05in}$ Linux/UNIX & $\hspace{.58in} \bullet \hspace{.05in}$ Windows & $\hspace{.09in} \bullet \hspace{.05in}$ OSX \\
%	\end{tabular}
%\end{left}}
%\largeskip

%\resumeitem{Software}{Familiar with: \footnotesize \begin{itemize}
%\item Networking software (Apache, Wireshark, Linux command-line tools)
%\item Design and Prototyping software (AutoCAD, Eagle, Fritzing)
%\item Math simulation software (Matlab, Maxima)
%\item \LaTeX
%\item Adobe Creative Suite
%\item Office Suites (Microsoft and open source)
%\end{itemize}}
%\largeskip

\resumeitem{Projects}{\footnotesize{ \newline
{\bf \href{http://wki.pe/\#!/faq}{Wki.pe}}\newline \textit{URL shortener for Wikipedia articles. Started as an early foray into databases. Single-page web app with PHP backend. Learned git, SEO techniques, adaptive HTML5. Brushed up on CSS, jQuery, SQL. Source code on \href{https://github.com/rabidaudio/wkipe}{GitHub}.}\newline

{\bf \href{http://blog.rabidaudio.com/search/label/car\%20audio}{Car Music Player}} [work in progress]\newline \textit{Raspberry Pi MP3 player embedded into my dashboard. Wrote player application from scratch in Python. Arduino I/O board with RS232 interface to Pi. Learned large Python programming with modules, serial communication. Brushed up on microprocessors.}\newline
\newline More projects and information on my blog: \scriptsize{\url{http://blog.rabidaudio.com}}
}}\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment}

\resumeitem{Sep 2012--Aug 2013}{\footnotesize{{\bf Norfolk Southern Corporation, Atlanta, Georgia}\newline Co-op, Distributed Systems/AIX. \textit{Worked closely with AIX administrators. Wrote automation scripts (perl/shell); worked with diagnostic reporting and resource inventory database; helped manage 10,000 sq. ft. datacenter; developed for and trained coworkers in SharePoint; developed application in Visio for visualizing datacenter layout; tweaked, deployed, and administered DokuWiki server.}}}
\shortskip

\resumeitem{Aug 2009--April 2012}{\footnotesize{{\bf Berry College Office of Information Technology, Mount Berry, Georgia} \newline Student Supervisor, Technical Support Desk. \textit{Provided technical support for faculty, staff, and students over phone, email, and in person; created and managed service requests; directed departmental calls.}}}
\shortskip

%\resumeitem{April 2008--Aug 2009}{\footnotesize{{\bf Customer Service Representative}, The UPS Store. \textit{Packed and moved boxes; worked POS and shipment system; sorted mail to private mailboxes; assisted in copy and print services; maintained general store upkeep.}}}
%\shortskip

\end{resumeblock}

\end{document}
