\documentclass[a4paper,12pt]{article}

\include{cv-commands2}
\begin{document}
\oddsidemargin=-1cm
\setmainfont

\header
{\LARGE{Sarah Elizabeth Ward}}
{}
{960 Diamond Circle\\LaFayette, GA  30728\\
{(423) 596--4151}\\sarahward0011@gmail.com}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Education}
\resumeitem{May 2011}{B.S. Mathematics, Berry College. {\footnotesize{\textit{Minors in Physics and Computer Science.}}}}
\largeskip

\resumeitem{Coursework}{{\footnotesize Embedded Microprocessors, Networks, Computer Architecture, Combinatorics, Object-Oriented Programming, Data Structures \& Algorithms.}}
\largeskip

\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Technical skills}

\resumeitem{Programming}{C, Python, Java, Scheme/Racket.}
\largeskip

\resumeitem{General}{Mathematica, Eclipse IDE, \LaTeX, Excel/MS Office.}
\largeskip

\resumeitem{Operating Systems}{Linux: CentOS, Ubuntu, Lubuntu; Windows: Vista, XP, 7.} %????
\largeskip
\end{resumeblock}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resumeblock}{Employment}

%\resumeitem{June 2011}{\footnotesize{{\bf Office Assistant}, Cherokee Regional Library System. \textit{Participated in internal control measures and general office duties.  Completed large projects requiring great attention to detail, including reviewing the previous fiscal year's bills/deposits and sorting the library system's library history archives.}}}
\resumeitem{June 2011}{\footnotesize{{\bf Office Assistant}, Cherokee Regional Library System.
\begin{itemize}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0cm}
\item Reviewed the previous fiscal year's bills and deposits for discrepancies.
\item Catalogued the library system's library history archives.
\item Analyzed Excel spreadsheets of inventory lost to storm damage.
\item Compared library and WorldCat databases to lists of removed inventory and made deletions.
\end{itemize}}}
\shortskip

%\resumeitem{2009--2011}{\footnotesize{{\bf Tutor}, Berry College. \textit{Tutored undergraduates in mathematics, computer science, and physics.}}}
\resumeitem{2009--2011}{\footnotesize{{\bf Tutor}, Berry College. 
\begin{itemize}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0cm}
\item Tutored undergraduates in mathematics, computer science, and physics.
\end{itemize}}}
\shortskip

%\resumeitem{2008--2011}{\footnotesize{{\bf Lab Assistant}, Berry College. \textit{Prepared physics labs and tested equipment. Repaired minor equipment malfunctions by soldering.}}}
\resumeitem{2008--2011}{\footnotesize{{\bf Lab Assistant}, Berry College. 
\begin{itemize}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0cm}
\item Assembled physics labs.
\item Tested equipment. 
\item Repaired minor equipment malfunctions by soldering.
\end{itemize}}}
\shortskip 

%\resumeitem{2008--2009}{\footnotesize{{\bf Student Supervisor}, Berry College. \textit{Supervised a team of 2-5 students in the campus dining hall performing time sensitive tasks.}}}
\resumeitem{2008--2009}{\footnotesize{{\bf Student Supervisor}, Berry College. 
\begin{itemize}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0cm}
\item Supervised two to five students.
\item Motivated teams of students to perform time sensitive tasks.
\item Welcomed customers and monitored the point of sale.
\end{itemize}}}
\shortskip

%\resumeitem{2007--2008}{\footnotesize{{\bf Student Worker}, Berry College. \textit{Performed general duties in the campus dining hall.}}}
\resumeitem{2007--2008}{\footnotesize{{\bf Student Worker}, Berry College.
\begin{itemize}
\setlength{\itemsep}{0cm}
\setlength{\parskip}{0cm}
\item Performed general duties in the campus dining hall.
\end{itemize}}}
\shortskip

\end{resumeblock}

\end{document}
